The paper on \Large \bf Blockchain Frontrunning

### 2018-08-28 frontrunning/Latex/sections/paper.tex
[frontrunning] fix miner transactions figure

\subsection{How are Blockchain Applications Vulnarable to front-running?}
\label{sec:Front Running on the Blockchains}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut.png}
\caption{This chart shows the miner behaviour on the time window that Status.im ICO was running. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}

>>>>

\subsection{How are Blockchain Applications Vulnarable to Front-running?}
\label{sec:Front Running on the Blockchains}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figures/Transactions_miners_while_status_ico_cut_only_icotx.png}
\caption{This chart shows the miners behaviour on the time window that Status.im ICO was running. \textit{Successful Transactions} are the transactions that led to deposit and generation of Status.im tokens and \textit{Failed Transactions} are the transactions to the token sale smart contract that failed to retrieve any tokens, for varias reasons.  It is clear that the number of successful transactions mined by F2Pool do not follow the random homogeneous pattern of the rest of the network. \label{fig:Transactions_miners_while_status_ico_cut}} 
\end{figure}
